When environmentally persistent pathogens transform good habitat into ecological traps

### 2016-02-17 Manuscript/manuscript.tex
Adding citation to Zenodo archived code

Continuous time stochastic simulations of the above model were implemented in the R language \cite{R2014} using the Gillespie algorithm \cite{Gillespie1977}.  Code is available at \\
\url{https://github.com/clint-leach/Metapop-Disease}.

@@

\subsection*{Data accessibility}
Simulation source code and generated data are available at \\  \url{https://github.com/clint-leach/Metapop-Disease}.

>>>>

Continuous time stochastic simulations of the above model were implemented in the R language \cite{R2014} using the Gillespie algorithm \cite{Gillespie1977}.  Code is available from the project's Github repository \cite{Leach2016}.

@@

\subsection*{Data accessibility}
Simulation source code and generated data are available on Github and archived at \url{http://dx.doi.org/10.5281/zenodo.46194}.
